### 2020-10-24 Thesis-Chapter3-Arguments.tex
Begin writing wicked problem strategy lessons

Lindblom's ``\ac{muddling-through}'' operates by taking successive steps chosen through comparative analysis. The
alternatives selected for comparison are defined relative to the status quo and are close enough to one another to be
able to be analyzed on the margin. This is done first out of practical necessity, due to our inability to rationally
predict policy outcomes, and second out of political realism, as non-incremental changes are usually politically
impossible to impose in a democratic system \cite{lindblom_muddling_1959}. \myfig{fig-muddling-through} illustrates this
method.

@@

Despite its strengths, \ac{incrementalism} has its weaknesses at addressing \acp{wicked-prob}. Its main weakness is its
lack of high level strategic analysis. It is incapable of drastic change, which is sometimes necessary. By Lindblom's
admission, it lacks a safeguard for consideration of all relevant values and may ``overlook excellent policies for no
other reason than that they are not suggested by the chain of successive policy steps leading up to the present''
\cite{lindblom_muddling_1959}. Analysis based only on one present ``status quo'' to the next can result in messy policy
that none are particularly fond of ("As Lindblom's sobriquet suggests, it often led to a considerable muddle''
\cite{feeley_judicial_2000}). Consider application of the \ac{CFAA} as an example of this kind of muddle
\cite{wolff_computer_2016}.

@@

- Avoid pitfalls of
  - Easy answers
    - EA mandates, complexity denial
  - Fallacies!
  - Bad results with long technical tails

@@

commission_tackling_2018:
- Strategies
  - Authoritative
  - Competitive
  - Collaborative
- Approaches
  - Linear problem solving
    - Ineffective! Several reasons, good breakdown. Dovetails with rozenshtein_wicked_2018.
  - Holistic problem solving: adaptive, innovative, flexible, cross-organizational
- Avoid
  - Narrow solutions

rozenshtein_wicked_2018:
- Approaches
  - Muddling through (he cites Charles E. Lindblom, just like feeley_judicial_2000!)
  - Risk management (--finally, something familiar to security experts!)
    - So, a broader view of security, inclusive of both public safety and information security
    - In this model, threat actors now include terrorists, CSAM distributors, organized crime
      - Add a new character? Evil Alice and evil Bob (Alex and Becca?)? This automatically raises to question of how to
          identify bad actors--AI (lee_detecting_2020)? PhotoDNA (microsoft_2020)? Government orders (warrants)? Could
          be useful.
    - I have already suggested adding government mandates to the traditional IS threat model
  - Imperfect solutions, like lawful hacking
  - Meanwhile, invest in knowledge production and improved relationships (like "cross-organizational" from
      commission_tackling_2018)
- Avoid
  - Easy answers ("narrow solutions" from commission_tackling_2018)
    - Such as EA mandates or "golden age of surveillance"-based denials

matyas_incommensurability_2018:
- Approaches to reducing incommensurability
  - Reduce gray area between rules and principles (i.e. keep laws up to date with technology)
  - Use transparency and accountability (through technical means)

feeley_judicial_2000:
- Classical analytic method ("linear" in commission_tackling_2018)
% 1. Classical analytic method; each step has its own approaches, e.g. cost-benefit analysis (loosely based on natural
% sciences)
%   (missing: Observe)
%   a. Define the problem (Orient)
%   b. Identify a goal (Orient)
%   c. Generate a range of alternatives for achieving that goal (Orient)
%   d. Select the alternative that seems most promising (Decide)
%   e. Implement the selected alternative (Act)
%   (missing: loop)
- Incremental intuitive decision making ("Muddling through" in rozenshtein_wicked_2018)
- The hermeneutic circle

>>>>

Lindblom's ``\ac{muddling-through}'' operates by taking successive steps chosen through comparative analysis. The
alternatives selected for comparison are defined relative to the status quo and are close enough to one another to be
able to be analyzed on the margin. This is done first out of practical necessity, due to our inability to rationally
predict policy outcomes, and second out of political realism, as non-incremental changes are usually politically
impossible to impose in a democratic system \cite{lindblom_muddling_1959}. The formality of the process varies;
policymakers may use this method consciously, with considerable comparative analysis, or unconsciously, led by
intuition. \myfig{fig-muddling-through} illustrates this method.

@@

Despite its strengths, \ac{incrementalism} has its weaknesses at addressing \acp{wicked-prob}. Its main weakness is its
lack of high level strategic analysis. It is incapable of drastic change, which is sometimes necessary. By Lindblom's
admission, it lacks a safeguard for consideration of all relevant values and may ``overlook excellent policies for no
other reason than that they are not suggested by the chain of successive policy steps leading up to the present''
\cite{lindblom_muddling_1959}. Analysis based only on one present ``status quo'' to the next can result in messy policy
that none are particularly fond of---``As Lindblom's sobriquet suggests, it often [leads] to a considerable muddle''
\cite{feeley_judicial_2000}. Consider application of the \ac{CFAA} as one such muddle \cite{wolff_computer_2016}.

@@

The \ac{classical-method} and \ac{incrementalism} are not the only styles of policymaking. They represent perhaps two
extremes on a spectrum of rational planning and intuitive muddling. Both have their strengths and weaknesses. One may
intuit that a reasonable strategy is the selective use of both approaches according to the situation, and indeed this
has also been formally suggested \cite{etzioni_scanning_1967}. However, even a combination of these methods does not
precisely suit all classes of wicked problems. Is a problem tame? Use the \ac{classical-method}. Is it wicked, but
strategically under control and relatively non-controversial? Use \ac{incrementalism}. Is it wicked, and lacking a
strategic response or highly controversial? What then?

There is no \ac{wicked-prob} handbook, but several sources offer advice.

\newcommand{\wickedtipsstart}{\begin{itemize}}
\newcommand{\wickedtip}[2]{ % Name, citation, description
    \item \textbf{#1} \nopagebreak

    \vspace{0.5\baselineskip} \parbox{\linewidth}{#2} \vspace{0.5\baselineskip}
}
\newcommand{\wickedtipsend}{\end{itemize}}

\wickedtipsstart

    \wickedtip{Reject Easy Answers}{
    }

    \wickedtip{Bring Everyone to the Table}{
    }

    \wickedtip{Embrace Flexible, Risk-Based Solutions}{
    }

    \wickedtip{Ensure Transparency}{
    }

\wickedtipsend

Rittel's follow-up research offers another tool: argument mapping.

% - Avoid pitfalls of
%   - Easy answers
%     - EA mandates, complexity denial
%   - Fallacies!
%   - Bad results with long technical tails

@@

commission_tackling_2018:
% - Strategies
%   - Authoritative
%   - Competitive
%   - Collaborative
% - Approaches
%   - Linear problem solving
%     - Ineffective! Several reasons, good breakdown. Dovetails with rozenshtein_wicked_2018.
%   - Holistic problem solving: adaptive, innovative, flexible, cross-organizational
% - Avoid
%   - Narrow solutions

rozenshtein_wicked_2018:
% - Approaches
  % - Muddling through (he cites Charles E. Lindblom, just like feeley_judicial_2000!)
  % - Risk management (--finally, something familiar to security experts!)
  %   - So, a broader view of security, inclusive of both public safety and information security
  %   - In this model, threat actors now include terrorists, CSAM distributors, organized crime
  %     - Add a new character? Evil Alice and evil Bob (Alex and Becca?)? This automatically raises to question of how to
  %         identify bad actors--AI (lee_detecting_2020)? PhotoDNA (microsoft_2020)? Government orders (warrants)? Could
  %         be useful.
  %   - I have already suggested adding government mandates to the traditional IS threat model
  % - Imperfect solutions, like lawful hacking
  % - Meanwhile, invest in knowledge production and improved relationships (like "cross-organizational" from
  %     commission_tackling_2018)
% - Avoid
%   - Easy answers ("narrow solutions" from commission_tackling_2018)
%     - Such as EA mandates or "golden age of surveillance"-based denials

matyas_incommensurability_2018:
- Approaches to reducing incommensurability
  - Reduce gray area between rules and principles (i.e. keep laws up to date with technology)
  % - Use transparency and accountability (through technical means)

% feeley_judicial_2000:
% - Classical analytic method ("linear" in commission_tackling_2018)
% % 1. Classical analytic method; each step has its own approaches, e.g. cost-benefit analysis (loosely based on natural
% % sciences)
% %   (missing: Observe)
% %   a. Define the problem (Orient)
% %   b. Identify a goal (Orient)
% %   c. Generate a range of alternatives for achieving that goal (Orient)
% %   d. Select the alternative that seems most promising (Decide)
% %   e. Implement the selected alternative (Act)
% %   (missing: loop)
% - Incremental intuitive decision making ("Muddling through" in rozenshtein_wicked_2018)
% - The hermeneutic circle
